---
title: "Comparison of two dots stimuli generated with same seed"
author: "Adrian Radillo"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_notebook:
    code_folding: hide
    css: styles.css
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

Load required libraries
```{r echo=FALSE}
library(data.table)
library(ggplot2)
library(htmlTable) # good ref here https://cran.r-project.org/web/packages/htmlTable/readme/README.html
```
```{r echo=FALSE}
dataTag <- "detail_11"
datafile <- paste("../data/",dataTag,".csv",sep='')
data <- fread(file=datafile, header=TRUE, sep=",")
# uncomment next line to inspect data table
#str(data)
```
# Stimulus used in this script
[Tag](https://github.com/aernesto/dotsStimExperiments/releases) name: **`r dataTag`**.  
Parameters of each dots stimulus:  
```{r echo=TRUE, results = 'asis'}
# row names for table output
rowNames <- list("stencilNumber", 
              "pixelSize",
              "diameter",
              "speed",
              "yCenter",
              "xCenter",
              "density",
              "direction",
              "coherence",
              "dotsDuration",
              "randSeedBase",
              "coherenceSTD")

# extract the parameter combinations for each stimulus
params <- data[,head(.SD,1), by = iter, .SDcols = stencilNumber:coherenceSTD]

matrixForTable <- as.matrix(params, rownames = "iter")
matrixForTable <- t(matrixForTable)
colnames(matrixForTable) <- c("stimulus 1","stimulus 2")

# output table
htmlTable(matrixForTable)

#dotsParam <- data.table(par= params, val = vals)
#kable(dotsParam, format='html', align = c('l','c'), digits = 0,
#      col.names = c("par","val"))
```


# Basic statistics of stimuli
In the table below,   
- `monitorFrames` doesn't count the monitor frames skipped before the first frame of the stimulus was displayed.  
- `timeSpan` is the difference between the last and the first `swapTime` value, in msec.
```{r echo=TRUE, results = 'asis'}
statsTable <- data[,.(presentedFrames = max(frameIdx), 
        monitorFrames = max(onsetFrame) - min(onsetFrame) + 1,
        timeSpan = round(1000 * (max(swapTime) - min(swapTime)))), 
     by=iter]

matrixForTable <- as.matrix(statsTable, rownames = "iter")
matrixForTable <- t(matrixForTable)
matrixForTable <- cbind(matrixForTable, matrixForTable[,2] - matrixForTable[,1])
colnames(matrixForTable) <- c("stimulus 1","stimulus 2", "difference")

# output table
htmlTable(matrixForTable)
```

Let's see if on the first frames that both stimuli got to present, the number of dots on each frame is the same. If the line below is constantly 0, it's a **WIN**!

```{r}
# max number of frames that both stimuli got to display
numOverlapFrames <- min(matrixForTable[1,1:2])
dotCount <- data[frameIdx <= numOverlapFrames,
     .(numDots = .N), 
     by = .(iter, frameIdx)]

# convert from long to wide format
dotCount <- dcast(dotCount, frameIdx ~ iter, value.var = c("iter", "numDots"))

```

```{r}
# plot settings
axes_labels_font <- 18
axes_font <- 15
lw <- 2

# plot command itself
ggplot(dotCount[,.(frameIdx, dotsCountDiff = numDots_2 - numDots_1)], 
       aes(x = frameIdx, y = dotsCountDiff)) +
  geom_line(size = lw) + 
  labs(title="Difference in dots count on each frame",
         subtitle=paste("From",dataTag,"dataset",sep=" ")) + 
  theme(plot.title=element_text(size=20,
                                    family="American Typewriter",
                                    lineheight=1.2),  # title
            axis.title.x=element_text(size=axes_labels_font),  # X axis title
            axis.title.y=element_text(size=axes_labels_font),  # Y axis title
            axis.text.x=element_text(size=axes_font),  # X axis text
            axis.text.y=element_text(size=axes_font))  # Y axis text




```


# Frame-by-frame comparison of dots positions 
Compute total distance between dots. It should be zero if all dots on all frames are identical across stimuli.

```{r}
subFrame <- data[frameIdx <= numOverlapFrames,.(iter, frameIdx, dotIdx, xpos, ypos)]

# the code below with dummyCol is ugly but I don't know how to improve it...
countRowsPerIter <- subFrame[,.(numRows = .N),by=iter]
dummyCol <- c(1:countRowsPerIter$numRows[1],1:countRowsPerIter$numRows[2])
subFrame <- cbind(subFrame, dummyCol)
distanceCheckFrame <- dcast(subFrame,
     dummyCol + frameIdx ~ iter, value.var = c("iter", "dotIdx","xpos","ypos"))

# check match of x positions across stimuli
identical(distanceCheckFrame$xpos_1, distanceCheckFrame$xpos_2)
# same for y positions
identical(distanceCheckFrame$ypos_1, distanceCheckFrame$ypos_2)
```

